\input{files/header}

\input{files/title}

\begin{document}

\nobibliography*
\bibliographystyle{apalike}

\input{files/titlepage}

\noindent We organize the course around the two flagship codes of our group. We use two codes to explore selected issues in software engineering, numerical methods, and computational engineering.

\begin{itemize}

\item \verb+respy+

We maintain a \verb+Python+ package for the simulation and estimation of a prototypical finite-horizon dynamic discrete choice model based on \citet{Keane.1997}.\vspace{0.3cm}

\begin{tabular}{ll}
\textbf{GitHub}		& \url{OpenSourceEconomics/respy}\\
\textbf{Docs}     & \url{respy.readthedocs.org}
\end{tabular}\vspace{0.3cm}

\item \verb+estimagic+

We maintain a \verb+Python+ package that helps to build high-quality and user-friendly implementations of (structural) econometric models. \verb+estimagic+ provides a consistent interface to a large set of global and local optimizers. Complicated optimizations can be monitored using an interactive browser-based dashboard.\vspace{0.3cm}

\begin{tabular}{ll}
\textbf{GitHub}		& \url{OpenSourceEconomics/estimagic}\\
\textbf{Docs}     & \url{estimagic.readthedocs.org}
\end{tabular}\vspace{0.3cm}
\end{itemize}

\noindent Throughout the course, we will make heavy use of \verb+Python+ and its \verb+SciPy+ ecosystem and \verb+Jupyter+ Notebooks. Basic knowledge of this toolchain is a prerequisite. There exist numerous introductory resources, and we provide a curated list at \url{ose-resources.readthedocs.io}. We will use \verb+zulip+ for all course communications, please be sure to join our workspace at \url{ose.zulipchat.com}.

\begin{itemize}

\item \textbf{Introduction}

We provide a general introduction to computational modeling in economics and our OpenSourceEconomics initiative. We outline opportunities for students to get involved.

\begin{itemize}
  \item \bibentry{OSE.2020a}
\end{itemize}

\item \textbf{Testing}

We discuss different types of automated tests and how they can be applied to scientific software projects. After presenting the basics, we show some examples in \verb+estimagic+ and \verb+respy+.

\begin{itemize}
  \item \bibentry{Okken.2017}
  \item \bibentry{Arbuckle.2010}
\end{itemize}


\item \textbf{Collaboration}

We introduce continuous integration features of \verb+GitHub+ and discuss workflows for different team sizes.

\begin{itemize}
  \item \bibentry{Chacon.2014}
  \item \bibentry{Bilschak.2016}
\end{itemize}

\item \textbf{Numerical optimization}

After a brief theoretical introduction to local and global optimization, students will solve straightforward optimization problems with \verb+scipy+. We then discuss the limitations of \verb+scipy.optimize+ in typical econometric workflows and introduce the students to the powerful optimization tools of the \verb+estimagic+ package.

\begin{itemize}
  \item \bibentry{Locatelli.2013}
  \item \bibentry{Nocedal.2006}
  \item \bibentry{Gabler.2019}
\end{itemize}

\item \textbf{Numerical derivatives}

After a brief introduction to numerical differentiation, we show how to calculate gradients, Jacobian and Hessian matrices using estimagic.

\begin{itemize}
  \item \bibentry{Brodtkorb.2019}
  \item \bibentry{Ridout.2009}
  \item \bibentry{Gabler.2019}
\end{itemize}

\item \textbf{Numerical integration}

We first introduce the participants to quadrature, Monte-Carlo, and Quasi-Monte-Carlo methods and provide them with (over)simplified guidelines to choose between the different methods. We then show the convergence speed of different approaches in a discrete choice dynamic programming model.

\begin{itemize}
  \item \bibentry{Davis.2007}
  \item \bibentry{Heiss.2008}
  \item \bibentry{Judd.2011}
\end{itemize}

\item \textbf{Discrete choice dynamic programming models}

We first outline the underlying economic, mathematical, and computational model. We then provide an overview of its applications in economics. Finally, we use \verb+respy+ to showcase the application of earlier lessons for numerical integration, parallelization strategies, version control, software testing, and continuous integration.

\begin{itemize}
\item \bibentry{OSE.2020}
\item \bibentry{Keane.2011d}
\item \bibentry{respy-1.0}
\end{itemize}

\item \textbf{Execution speed}

Execution speed \verb+Python+ is often called a slow language. Nevertheless, it is one of the most widely used languages for high-performance computing. We teach students how to make their \verb+Python+ code fast with \verb+numpy+ and \verb+numba+ and how to parallelize it using \verb+multiprocessing+ and \verb+joblib+. After the students solve simple examples, we look at some implementations is \verb+respy+.


\begin{itemize}
\item \bibentry{Gorelick.2014}
\item \bibentry{Lanaro.2017}
\end{itemize}


\end{itemize}


\bibliographystyle{apalike}
\nobibliography{../submodules/bibliography/literature}

\end{document}
